Specific taxa differentiate proximal and distal microbiota in the unprepped

### 2017-07-11 submission/manuscript.Rmd
discussion almost fixed

>>>>

The _Fusobacterium_ species _nucleatum_ and _varium_ have been commonly isolated from mucosal biopsies of patients with IBD (cite). Laboratory experiments with these isolates have shown that disease-isolated _F. nucleatum_ are more invasive and stimulate more TNF-a production than strains from healthy individuals (@Strauss2011), suggesting the bacteria may increase inflammation in the gut as well (cite - Dharmani 2011). _F. varium_ isolated from UC patients caused colonic ulcers in an experimental mouse model (Ohkusa 2003). _F. varium_ was only detected in 3 of our study participants and two of those samples were isolated form the proximal mucosa (cite figure). Although there is low occurrance in our study, _F. varium_ is most commonly isolated from UC patient biopsies from the ileum or cecum (cite), suggesting this species may exhibit preference for the different environmental conditions of these gastrointestinal sites. Further work will assess how gut environment may select for species which then cause localized disease.
